

\begin{thebibliography}{}



\bibitem{effps} R. Mohan and A. Valada. (2020). \textit{EfficientPS: Efficient Panoptic Segmentation}. \url{http://panoptic.cs.uni-freiburg.de/}

\bibitem{dl-book} I. Goodfellow, Y. Bengio and A. Courville. (2016). \textit{Deep Learning}. MIT Press. \url{http://www.deeplearningbook.org/}

%% soms hoofdstuk 1, soms hfst 9: fix dit in de tekst 


\bibitem{first} \url{http://historyofinformation.com/detail.php?entryid=782}

\bibitem{mcc} McCulloch, W. S., \& Pitts, W. (1943). A logical calculus of the ideas immanent in nervous activity. The bulletin of mathematical biophysics, 5(4), 115-133.

\bibitem{percep} Rosenblatt, F. (1958). \textit{The perceptron: A probabilistic model for information storage and organization in the brain}. Psychological Review, 65(6), 386–408. https://doi.org/10.1037/h0042519

\bibitem{med} https://towardsdatascience.com/mcculloch-pitts-model-5fdf65ac5dd1

\bibitem{fullpic} \url{https://www.linkedin.com/pulse/deep-learning-nutshell-part-1-ankit-agarwal/}

\bibitem{convnet} Convolutional Networks and Applications in Vision. Yann LeCun, Koray Kavukcuoglu and Cl\'ement Farabet

\bibitem{dl-lecun} LeCun, Y., Bengio, Y. \& Hinton, G. \textit{Deep learning}. Nature 521, 436–444 (2015). \url{https://doi.org/10.1038/nature14539}

\bibitem{jap} K. Fukushlma, Neural network model for a mechamsm
of pattern recognmon unaffected by shift m
posltlon--neocogmtron--, Trans Inst electromcs commun
Enors Japan 62-A, 658-665 (1979) (In Japanese)

\bibitem{neocog} K. Fukushima, \textit{Neocognitron a self-organizing neural
network model for a mechanism of pattern recognition
unaffected by shift in position}, Biological Cybernetics 36,
193-202 (1980)

\bibitem{sch} Schmidhuber, Jürgen (2015). "Deep Learning". Scholarpedia. \url{http://www.scholarpedia.org/article/Deep_Learning}

\bibitem{about-fuku} "Kunihiko Fukushima". The Franklin Institute. \url{https://www.fi.edu/laureates/kunihiko-fukushima}

\bibitem{fuzzy} \url{http://personalpage.flsi.or.jp/fukushima/index-e.html}

\bibitem{history} \url{https://www.import.io/post/history-of-deep-learning/}

\bibitem{83} Fukushima, K. (2019). Efficient IntVec: High recognition rate with reduced computational cost. Neural Networks, 119, 323-331.

\bibitem{hubel} Hubel, D.H., Wiesel, T.N. \textit{Receptive fields, binocular interaction
and functional architecture in cat's visual cortex}. J. Physiol.
(London) 160, 106-154 (1962)

\bibitem{wiesel} Hubel, D.H., Wiesel, T.N. \textit{Receptive fields and functional architecture in two nonstriate visual area (18 and 19) of the cat}. J.
Neurophysiol. 28, 229-289 (1965)


%% lecun sec

\bibitem{bio} \url{http://yann.lecun.com/ex/bio.html}

\bibitem{cunpic} \url{https://www.ipam.ucla.edu/news/lecun-wins-a-m-turing-award/}

\bibitem{ocr} Y. LeCun, B. Boser, J. S. Denker, D. Henderson, R. E. Howard,
W. Hubbard, and L. D. Jackel, “Handwritten digit recognition with a
back-propagation network,” in NIPS 1989.

\bibitem{gap} \url{https://dataconomy.com/2017/04/history-neural-networks/}

\bibitem{fath} \url{https://www.acm.org/media-center/2019/march/turing-award-2018}


%%%% math sec

\bibitem{wolf} \url{https://mathworld.wolfram.com/Convolution.html}

\bibitem{tor} \url{https://www.slideshare.net/Alexdfar/origin-adn-history-of-convolution}

\bibitem{stanf} \url{http://ufldl.stanford.edu/tutorial/supervised/FeatureExtractionUsingConvolution/}

\bibitem{dsp} \url{https://www.analog.com/media/en/technical-documentation/dsp-book/dsp_book_Ch6.pdf}

\bibitem{visual} \url{https://setosa.io/ev/image-kernels/}







\bibitem{radiol} \url{https://link.springer.com/article/10.1007/s13244-018-0639-9}

\bibitem{ilsvrc} \url{https://link-springer-com.dianus.libr.tue.nl/article/10.1007/s11263-015-0816-y}


\bibitem{histdoc} \url{https://ieeexplore.ieee.org/abstract/document/8270092?casa_token=q_AXk5mKF_oAAAAA:lpGuigrjJYCVpxurTC3XeGgTYOcqJeedVwBMeXIdUbIhNeX7Ye2_dzHXRHlLc12ulZy6NmVS}


\bibitem{face} \url{https://ieeexplore.ieee.org/abstract/document/554195?casa_token=UpfMNOXCsSMAAAAA:z2fxgzBEbbIymhVxAnF4t_VRfNBylbTzHpwGQ028KJHM-nThg8WOxxnvAl1qQerBsiJBP6M5}

\bibitem{express} \url{https://www.sciencedirect.com/science/article/pii/S0893608003001151?casa_token=3LVC6qtWjF0AAAAA:oMkG3qFftEKJTG4XJocu28A7B8aPA6gqWKGH0FBuoYNS_I3Pgkz1FoVc7ZP0B7iRop0ylTC9_A}

\bibitem{illu} \url{https://ieeexplore.ieee.org/abstract/document/7091490?casa_token=feOE4QN7vrwAAAAA:aiZXs7_5whx8o8AEP9SfLUO4TNRYV45v6b3TCwjY1J6Je09jHbwbkz-uvlGTVrJvJiJ-84yg}

\bibitem{brain} H. Cecotti and A. Graser, "Convolutional Neural Networks for P300 Detection with Application to Brain-Computer Interfaces," in IEEE Transactions on Pattern Analysis and Machine Intelligence, vol. 33, no. 3, pp. 433-445, March 2011, doi: 10.1109/TPAMI.2010.125. \url{https://ieeexplore.ieee.org/abstract/document/5492691?casa_token=6WvMv0ZWR6AAAAAA:orzQB5P927bz9wUPxRZZtEY9a2H3HGFfNRH-N5j45Bi2z9FjF3vWozWNuk92PnkJf5FaKMqI}

\bibitem{cancer} \url{https://link.springer.com/article/10.1007/s10120-018-0793-2}

\bibitem{fake} \url{https://thispersondoesnotexist.com/}

\bibitem{climate} \url{https://arxiv.org/abs/1605.01156}

\bibitem{speech} \url{https://ieeexplore-ieee-org.dianus.libr.tue.nl/document/6639344}

\bibitem{nlp} \url{https://www.researchgate.net/profile/Loic_Barrault/publication/303822179_Very_Deep_Convolutional_Networks_for_Natural_Language_Processing/links/5772506308aeeec38953dd26/Very-Deep-Convolutional-Networks-for-Natural-Language-Processing.pdf}



















\end{thebibliography}